\blue{Numerical Investigation of Multi-Fluid Flows through Dual Saturated-Unsaturated Porous Media - change the title to something close to the main topic of the manuscript ... something with viscous flow instability or viscous fingering)}

### 2017-06-25 Papers/ViscousInstabilities/article_figure2.tex
working-updated
changes on progress

%\begin{figure}[ht] 
%\begin{center}
%\includegraphics[width=0.75\linewidth, height=7cm]{2b2_P1DGP2_perm} 
%\caption{Caption 1}
%\label{fig:subim1}
%\end{center}

%\begin{center}
%\includegraphics[width=0.75\linewidth, height=7cm]{2b2_P1DGP2_mesh} 
%\caption{Caption 1}
%\label{fig:subim1}
%\end{center}

%\begin{center}
%\centering
%\includegraphics[width=0.75\linewidth, height=6cm]{2b2_P1DGP2_plot}
%\caption{Caption 3}
%\label{fig:subim3}
%\end{center}

%\caption{Caption for this figure with two images}
%\label{fig:image1}
%\end{figure}
%\pagebreak
%\clearpage

%\begin{figure}[ht] 
%\begin{center}
%\includegraphics[width=0.75\textwidth]{./Pics/phase_vol_frac_uni_perm_1.pdf}
%\caption{This is the case where the initially piston shape front is collapsing and starts forming fingers in an unstructured domain with uniform permeability (3000 elements, K=1, MR=5).}
%\label{fig:simple_case}
%\end{center}
%\end{figure}

%\begin{figure}[ht] 
%\begin{center}
%\subfigure[Initial and boundary conditions]{\includegraphics[width=0.65\textwidth]{./Pics/2b2_P1DGP2.pdf}\label{a}}
%\subfigure[Plots of velocity magnitude, pressure and phase volume fraction]{\includegraphics[width=0.6\textwidth]{./Pics/2b2_P1DGP2_plot.pdf}\label{b}}
%\caption{This is the first test-case of a region with four squares of constant permeabilities K of $1$ at the the blue region and $2.5$ at the red region. The mesh is unstructured and fixed with 5000 elements. Fluid $1$ is introduced from the right hand side at a constant velocity of u = $1$, This test-case is based on the experimental work of \citet{evans_1994}.}
%\label{fig:square}
%\end{center}
%\end{figure}

%\begin{figure}[ht] 
%   \vbox{
%       \hbox{\includegraphics[width=.5\textwidth]{./Pics/2b2_P1DGP2.pdf}
%             \includegraphics[width=.5\textwidth]{./Pics/2b2_P1DGP2_plot.pdf}}
%       \hbox{\hspace{3cm}(a) \PN[1]{2} \hspace{4.cm} (b)\PNDG[2]{1}}}
%\caption{2D representation of the element pairs presented in this work. Shaded areas denote control volumes (in which saturation is   stored), black points% represent the pressure nodes and white points the velocity nodes. Note that in (b) velocity and pressure nodes overlap in the triangles' vertices.}
%    \label{fem_cv_represent_a}
%\end{figure}

%%%%
%%%%  FIGURE
%%%%
\begin{figure}[ht] 
\vbox{
\hbox{\hspace{2.5cm}
\includegraphics[width=.6\textwidth]{./Pics/2b2_P1DGP2.pdf} 
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (a)  
}
\vspace{0.5cm}
\hbox{\hspace{2.5cm}
\includegraphics[width=.6\textwidth]{./Pics/2b2_P1DGP2_plot.pdf}
}
\vspace{1.0cm}
\hbox{\hspace{5.0cm} (b)  
}}     
\caption{2D representation of the element pairs presented in this work. Shaded areas denote control volumes (in which saturation is stored), black points represent the pressure nodes and white points the velocity nodes. Note that in (b) velocity and pressure nodes overlap in the triangles' vertices.}
\label{fem_cv_represent_a}
\end{figure}

%%%%
%%%%  FIGURE
%%%%
\begin{figure}[ht] 
\vbox{
\hbox{\hspace{1.5cm}
\includegraphics[width=.75\textwidth]{./Pics1/2b2_wi_fine/2b2_whole_in_fine_perm_1.pdf} 
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (a) map of permeabilties K  
}
\vspace{0.25cm}
\hbox{\hspace{1.5cm}
\includegraphics[width=.75\textwidth]{./Pics1/2b2_wi_fine/2b2_whole_in_fine_250_2.pdf}
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (b) flow at t=250  
}
\vspace{0.25cm}
\hbox{\hspace{1.5cm}
\includegraphics[width=.75\textwidth]{./Pics1/2b2_wi_fine/2b2_whole_in_fine_3000_1.pdf}
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (b) flow at t=3000  
}
}     
\caption{Using unstructured but fixed mesh the domain is devide into $4$ different regions of different permeabilities as these are represented in the figures above}
\label{fem_cv_represent_a}
\end{figure}

%%%%
%%%%  FIGURE
%%%%
\begin{figure}[ht] 
\vbox{
\hbox{\hspace{1.5cm}
\includegraphics[width=.75\textwidth]{./Pics1/mr1_fixed/mr1_fixed_100_2.pdf} 
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (a) MR1 at t = 100 (start)   
}
\vspace{0.25cm}
\hbox{\hspace{1.5cm}
\includegraphics[width=.75\textwidth]{./Pics1/mr10_fixed/mr10_fixed_100_1.pdf}
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (b) MR10 at t = 100 (start)  
}
}     
\caption{Comparing the the MR1 and MR10 cases using fixed mesh in the beggining of the simulation.}
\label{fig:6a}
\end{figure}

%%%%
%%%%  FIGURE
%%%%
\begin{figure}[ht] 
\vbox{
\hbox{\hspace{1.5cm}
\includegraphics[width=.75\textwidth]{./Pics1/mr1_fixed/mr1_fixed_middle_1.pdf} 
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (a) MR1 at t = 1500 (middle)   
}
\vspace{0.25cm}
\hbox{\hspace{1.5cm}
\includegraphics[width=.75\textwidth]{./Pics1/mr10_fixed/mr10_fixed_middle_1.pdf}
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (b) MR10 at t = 1500 (middle)  
}
}     
\caption{Comparing the the MR1 and MR10 cases using fixed mesh in the middle of the simulation.}
\label{fig:6b}
\end{figure}

%%%%
%%%%  FIGURE
%%%%
\begin{figure}[ht] 
\vbox{
\hbox{\hspace{1.5cm}
\includegraphics[width=.75\textwidth]{./Pics1/mr1_fixed/mr1_fixed_middle_1.pdf} 
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (a) MR1 at t = 3000 (end)   
}
\vspace{0.25cm}
\hbox{\hspace{1.5cm}
\includegraphics[width=.75\textwidth]{./Pics1/mr10_fixed/mr10_fixed_middle_1.pdf}
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (b) MR10 at t = 3000 (end)  
}
}     
\caption{Comparing the the MR1 and MR10 cases using fixed mesh in the end of the simulation.}
\label{fig:6c}
\end{figure}

%%%%
%%%%  FIGURE
%%%%
\begin{figure}[ht] 
\vbox{
\hbox{\hspace{3.5cm}
\includegraphics[width=.5\textwidth]{./Pics1/Saffman_homogeneous_MR3/saffman_homo_fixed_1.pdf} 
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (a) Hell-Shaw cell domain   
}
\vspace{0.25cm}
\hbox{\hspace{3.5cm}
\includegraphics[width=.5\textwidth]{./Pics1/Saffman_homogeneous_MR3/saffman_homo_fixed_250.pdf}
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (b) flow at t=250  
}
}     
\caption{This is a description of a Hele-Shaw experimental domain, showing the source and sink term as this is implied in this test-case followed by a screenshot of the flow at time, t=250(b). More screenshot follow that describe the progression of the flow in Fig.\ref{fig:1b_homoheleshaw_3} and Fig.\ref{fig:1c_homoheleshaw_3}}
\label{fig:1a_homoheleshaw_3}
\end{figure}

%%%%
%%%%  FIGURE
%%%%
\begin{figure}[ht] 
\vbox{
\hbox{\hspace{3.5cm}
\includegraphics[width=.5\textwidth]{./Pics1/Saffman_homogeneous_MR3/saffman_homo_fixed_1000.pdf} 
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (a) flow at t=1000   
}
\vspace{0.25cm}
\hbox{\hspace{3.5cm}
\includegraphics[width=.5\textwidth]{./Pics1/Saffman_homogeneous_MR3/saffman_homo_fixed_2500.pdf}
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (b) flow at t=2500  
}
}     
\caption{Following Fig.\ref{fig:1a_homoheleshaw_3} as the flow progress, t=1000(a), a tip start to appears, at t=2500(b)}
\label{fig:1b_homoheleshaw_3}
\end{figure}

%%%%
%%%%  FIGURE
%%%%
\begin{figure}[ht] 
\vbox{
\hbox{\hspace{3.5cm}
\includegraphics[width=.5\textwidth]{./Pics1/Saffman_homogeneous_MR3/saffman_homo_fixed_3500.pdf} 
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (a) flow at t=3500   
}
\vspace{0.25cm}
\hbox{\hspace{3.5cm}
\includegraphics[width=.5\textwidth]{./Pics1/Saffman_homogeneous_MR3/saffman_homo_fixed_end_1.pdf}
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (b) flow at t=end  
}
}     
\caption{This tip will become sharper at t=3500(a) as it approaches the area where sink term exist and finally at t=end(b) it will be absorbed.}
\label{fig:1c_homoheleshaw_3}
\end{figure}

%%%%
%%%%  FIGURE
%%%%
\begin{figure}[ht] 
\vbox{
\hbox{\hspace{3.5cm}
\includegraphics[width=.5\textwidth]{./Pics1/Saffman_homogeneous/saffman_homo_fixed_1.pdf} 
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (a) Hell-Shaw cell domain   
}
\vspace{0.25cm}
\hbox{\hspace{3.5cm}
\includegraphics[width=.5\textwidth]{./Pics1/Saffman_homogeneous/saffman_homo_fixed_250_1.pdf}
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (b) flow at t=250  
}
}     
\caption{This is a description of a Hele-Shaw experimental domain, when MR=$10$ showing the source and sink term as this is implied in this test-case followed by a screenshot of the flow at time, t=250(b). Screenshot will follow that describe the progression of the flow in fig.\ref{fig:2b_homoheleshaw_10} and fig.\ref{fig:2c_homoheleshaw_10}}
\label{fig:2a_homoheleshaw_10}
\end{figure}

%%%%
%%%%  FIGURE
%%%%
\begin{figure}[ht] 
\vbox{
\hbox{\hspace{3.5cm}
\includegraphics[width=.5\textwidth]{./Pics1/Saffman_homogeneous/saffman_homo_fixed_1000.pdf} 
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (a) flow at t=1000   
}
\vspace{0.25cm}
\hbox{\hspace{3.5cm}
\includegraphics[width=.5\textwidth]{./Pics1/Saffman_homogeneous/saffman_homo_fixed_4000.pdf}
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (b) flow at t=4000  
}
}     
\caption{As the flow progress at t=1000(a) the front still remains uniform. The first break down of the front is happening at t=4000(b) where $3$ tips start to come out of the main flow.}
\label{fig:2b_homoheleshaw_10}
\end{figure}

%%%%
%%%%  FIGURE
%%%%
\begin{figure}[ht]
\vbox{
\hbox{\hspace{3.5cm}
\includegraphics[width=.5\textwidth]{./Pics1/Saffman_homogeneous/saffman_homo_fixed_1000.pdf} 
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (a) flow at t=1000   
}
\vspace{0.25cm}
\hbox{\hspace{3.5cm}
\includegraphics[width=.5\textwidth]{./Pics1/Saffman_homogeneous/saffman_homo_fixed_4000.pdf}
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (b) flow at t=4000  
}
}     
\caption{As the flow progress at t=1000(a) the front still remains uniform. The first break down of the front is happening at t=4000(b) where $3$ tips start to come out of the main flow.}
\label{fig:2b_homoheleshaw_10}
\end{figure}

%%%%
%%%%  FIGURE
%%%%
\begin{figure}[ht]
\vbox{
\hbox{\hspace{3.5cm}
\includegraphics[width=.5\textwidth]{./Pics1/Saffman_homogeneous/saffman_homo_fixed_6000.pdf} 
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (a) flow at t=6000   
}
\vspace{0.25cm}
\hbox{\hspace{3.5cm}
\includegraphics[width=.5\textwidth]{./Pics1/Saffman_homogeneous/saffman_homo_fixed_end_1.pdf}
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (b) flow at t=end   
}
}     
\caption{Finger are now more obvious as the flow progress and the tip-splitting mechanism becomes stronger at t=6000(a) as it approaches the area where sink term exist and finally at t=end(b) it will be absorbed.}
\label{fig:2c_homoheleshaw_10}
\end{figure}

%%%%
%%%%  FIGURE
%%%%
\begin{figure}[ht] 
\vbox{
\hbox{\hspace{3.5cm}
\includegraphics[width=.5\textwidth]{./Pics1/Saffman_heterogeneous/saffman_heter_fixed_1.pdf} 
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (a) Hell-Shaw cell domain   
}
\vspace{0.25cm}
\hbox{\hspace{3.5cm}
\includegraphics[width=.5\textwidth]{./Pics1/Saffman_heterogeneous/saffman_heter_fixed_500.pdf}
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (b) flow at t=250     
}
}     
\caption{This is a description of a heterogeneous Hele-Shaw experimental domain, when MR=$10$ showing the source and sink term as this is implied in this test-case followed by a screenshot of the flow at time, t=500(b). Screenshot will follow that describe the progression of the flow in fig.\ref{fig:3b_heteheleshaw_10} and fig.\ref{fig:3c_heteheleshaw_10}}
\label{fig:3a_heteheleshaw_10}
\end{figure}

%%%%
%%%%  FIGURE
%%%%
\begin{figure}[ht] 
\vbox{
\hbox{\hspace{3.5cm}
\includegraphics[width=.5\textwidth]{./Pics1/Saffman_heterogeneous/saffman_heter_fixed_2000.pdf} 
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (a) flow at t=2000   
}
\vspace{0.25cm}
\hbox{\hspace{3.5cm}
\includegraphics[width=.5\textwidth]{./Pics1/Saffman_heterogeneous/saffman_heter_fixed_3000.pdf}
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (b) flow at t=3000     
}
}     
\caption{As the flow progress at t=2000(a) but now the front is completely unstable as it has already collapsed forming many finger formations. Finger formations are more aggressive as the simulations progress, t=3000(b) where many tips have already start to develop out of the main flow.}
\label{fig:3b_heteheleshaw_10}
\end{figure}

%%%%
%%%%  FIGURE
%%%%
\begin{figure}[ht] 
\vbox{
\hbox{\hspace{3.5cm}
\includegraphics[width=.5\textwidth]{./Pics1/Saffman_heterogeneous/saffman_heter_fixed_6000.pdf} 
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (a) flow at t=6000    
}
\vspace{0.25cm}
\hbox{\hspace{3.5cm}
\includegraphics[width=.5\textwidth]{./Pics1/Saffman_heterogeneous/saffman_heter_fixed_24000.pdf}
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (b) flow at t=24000     
}
}     
\caption{At t=6000(a), one main finger have already reached the area where sink exists as they have develop much faster than the rest of the fingers. At t=24000(b) there are two main fingers that now have developed and drive the flow forwards.}
\label{fig:3c_heteheleshaw_10}
\end{figure}
%{./Pics/P1DG-P2_element_type} 
%{./Pics/4r_po_adapt_fine_125_mesh} 
%{./Pics/4r_po_adapt_fine_100_mesh}

%%%%
%%%%  FIGURE
%%%%
\begin{figure}[ht] 
\vbox{
\hbox{\hspace{3.5cm}
\includegraphics[width=.5\textwidth]{./Pics/map_of_boundaries.pdf} 
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (a) map of permeabilties K   
}
\vspace{0.25cm}
\hbox{\hspace{3.5cm}
\includegraphics[width=.5\textwidth]{./Pics/4r_po_adapt_fine_125_mesh.pdf}
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (b)      
}
}     
\caption{(a) describes the initial and boundary conditions as these are applied in this set of simulations. Below (b) the unstructured and fixed mesh can been seen and there is a colored representation of permeabilities.}
\label{fig:testcase_heter_domain}
\end{figure}

>>>>

%%%%%%%%%%%%%%%%
%%% Figure 1 %%%
%%%%%%%%%%%%%%%%
%\begin{figure}[h]
%\begin{center}
%\includegraphics[width=.5\textwidth]{./Pics/P1DGP2.pdf}
%\caption{2D representation of the $P_{1}DGP_{2}$ element pairs used in this work. Shaded areas denote control volumes (in which saturation field is stored), blue points represent the pressure nodes and white points the velocity nodes.}
%\label{fig:fem_cv}
%\end{center}
%\end{figure}
%\clearpage

%%%%%%%%%%%%%%%%
%%% Figure 2 %%%
%%%%%%%%%%%%%%%%
%\begin{figure}[h] 
%\begin{center}
%\includegraphics[width=.5\textwidth]{./Pics/element_n.pdf}
%\caption{Porosity $\phi_{i}$, and permeability $K_{i}$ are associated to the elements. The velocity and pressure are associated to the element corners and the mid-points as described in fig.\ref{fig:fem_cv}; three CVs fit into a $2$D element. Saturation and saturation-dependent variables are stored CV-wise.}
%\label{fig:fem_elem}
%\end{center}
%\end{figure}
%\clearpage

%%%%
%%%%  FIGURE 
%%%%
\begin{figure}[h]
\centering
\vbox{\includegraphics[width=.5\textwidth]{./Pics/P1DGP2.pdf}}
\caption{2D representation of \PN[1]{2} element pairs used in this work. Shaded areas denote control volumes across two contiguous elements. Blue and white circles represent pressure and velocity nodes, respectively.}
\label{fig:fem_cv}
\end{figure}

\clearpage

%%%%
%%%%  FIGURE
%%%%
\begin{figure}[h]
\centering
\vbox{\includegraphics[width=.75\textwidth]{./Pics/element_n.pdf}}
\caption{This is a graphical representation of two different element types. Element A is the \PN[1]{2}, while element B is the \PN[1]{1}. Porosity $\phi_{i}$ and permeability $K_{i}$ are CV-wise quantities, whereas velocity and pressure are primarily represented in FE space. Scalar fields (such saturation, density, viscosity etc) are also represented in CV space.}
\label{fig:fem_elem}
\end{figure}
\clearpage

%%%%
%%%%  FIGURE 1
%%%%
\begin{figure}[h]
\centering
\vbox{\includegraphics[width=0.75\textwidth]{./Pics/phase_vol_frac_uni_perm_1.pdf}}
\caption{Schematics of formation of flow instabilities during injection of a pure low viscosity fluid (red) into a domain saturated with a second fluid (dark blue). The ratio of viscosity between the two fluids is 5. In this case, the initially piston shape front collapses leading to the formation of several fingers.}
\label{fig:simple_case}
\end{figure}
\clearpage

%%%%
%%%%  FIGURE 4
%%%%
\begin{figure}[ht] 
\vbox{
\hbox{\hspace{-0.3cm}
\includegraphics[width=.8\textwidth]{./Pics1/2b2_wi_fine/2b2_whole_in_fine_perm_1.pdf} 
}
\vspace{0.0cm}
\hbox{\hspace{3.5cm} (a) map of permeabilities ($\mathbf{K}$)
}
\vspace{0.25cm}
\hbox{\hspace{1.5cm}
\includegraphics[width=.9\textwidth]{./Pics1/2b2_wi_fine/2b2_whole_in_fine_250_2.pdf}
}
\vspace{0.0cm}
\hbox{\hspace{4.5cm} (b) flow at t=250  
}
\vspace{0.25cm}
\hbox{\hspace{1.5cm}
\includegraphics[width=.65\textwidth]{./Pics1/2b2_wi_fine/2b2_whole_in_fine_3000_1.pdf}
}
\vspace{0.0cm}
\hbox{\hspace{4.0cm} (c) flow at t=3000  
}
}     
\caption{Model validation of fluid displacement in heterogeneous porous media: (a) the domain is divided into four subdomains with prescribed synthetic permeability, $\mathbf{K}_{1}=1$ and $\mathbf{K}_{2}=2.5$; (b-c) snapshots of saturation (displacing fluid) field at $t=250$ and $t=3000$ sec. The domain is discretised in $5960$ \PN[1]{2} elements. }
\label{fem_cv_represent_a}
\end{figure}
\clearpage

\begin{comment}
%%%
%%% FIGURE
%%%
\begin{landscape}
  \begin{figure}[ht]
    \vbox{ 
      \hbox{\includegraphics[width=.55\textwidth]{./Pics1/mr1_fixed/mr1_fixed_100_2.pdf}
            \includegraphics[width=.55\textwidth]{./Pics1/2b2_wi_fine/2b2_whole_in_fine_250_2.pdf}
            \includegraphics[width=.55\textwidth]{./Pics1/mr1_fixed/mr1_fixed_middle_1.pdf} }
      \vspace{0.cm}
      \hbox{\includegraphics[width=.55\textwidth]{./Pics1/2b2_wi_fine/2b2_whole_in_fine_3000_1.pdf}
            \includegraphics[width=.55\textwidth]{./Pics1/mr1_fixed/mr1_fixed_middle_1.pdf}}}
\caption{\red{THIS IS JUST FOR OUR OWN COMPARISON ... IT DOESN'T SEEM TO MATCH ... }}
\label{fem_cv_represent_abc}
\end{figure}
\end{landscape}
\clearpage
%%%
%%%
%%%
\end{comment}

%%%
%%% FIGURE
%%%
\begin{landscape}
  \begin{figure}[ht]
    \vbox{ 
      \hbox{\includegraphics[width=.45\textwidth]{./Pics1/mr1_fixed/mr1_fixed_100_2.pdf}
            \includegraphics[width=.45\textwidth]{./Pics1/mr1_fixed/mr1_fixed_middle_1.pdf} 
            \includegraphics[width=.57\textwidth]{./Pics1/mr1_fixed/mr1_fixed_end_2.pdf} }
      \hbox{\hspace{8.0cm} (a) VR = 1}
      \vspace{1cm}
      \hbox{\includegraphics[width=.45\textwidth]{./Pics1/mr10_fixed/mr10_fixed_100_1.pdf}
            \includegraphics[width=.45\textwidth]{./Pics1/mr10_fixed/mr10_fixed_middle_1.pdf}
            \includegraphics[width=.57\textwidth]{./Pics1/mr10_fixed/mr10_fixed_end_2.pdf} }
      \hbox{\hspace{8.0cm} (b) VR = 10  }}
\caption{Initial model validation: snapshots of numerical simulations performed with VR=1 and VR=10. The domain contains $4700$ elements.}
\label{fem_cv_represent_a}
\end{figure}
\end{landscape}
\clearpage
%%%
%%%
%%%

\begin{comment}
%%%%
%%%%  FIGURE
%%%%
\begin{figure}[ht] 
\vbox{
\hbox{\hspace{1.5cm}
\includegraphics[width=.85\textwidth]{./Pics1/mr1_fixed/mr1_fixed_100_2.pdf} 
}
\vspace{0.0cm}
\hbox{\hspace{4.0cm} (a) MR1 at t = 100 (start)   
}
\vspace{0.25cm}
\hbox{\hspace{1.5cm}
\includegraphics[width=.85\textwidth]{./Pics1/mr10_fixed/mr10_fixed_100_1.pdf}
}
\vspace{0.0cm}
\hbox{\hspace{4.0cm} (b) MR10 at t = 100 (start)  
}
}     
\caption{Comparing the the MR1 and MR10 cases using fixed mesh in the beggining of the simulation.}
\label{fig:6a}
\end{figure}
\clearpage

%%%%
%%%%  FIGURE
%%%%
\begin{figure}[ht] 
\vbox{
\hbox{\hspace{1.5cm}
\includegraphics[width=.85\textwidth]{./Pics1/mr1_fixed/mr1_fixed_middle_1.pdf} 
}
\vspace{0.0cm}
\hbox{\hspace{4.0cm} (a) MR1 at t = 1500 (middle)   
}
\vspace{0.25cm}
\hbox{\hspace{1.5cm}
\includegraphics[width=.85\textwidth]{./Pics1/mr10_fixed/mr10_fixed_middle_1.pdf}
}
\vspace{0.0cm}
\hbox{\hspace{4.0cm} (b) MR10 at t = 1500 (middle)  
}
}     
\caption{Comparing the the MR1 and MR10 cases using fixed mesh in the middle of the simulation.}
\label{fig:6b}
\end{figure}
\clearpage

%%%%
%%%%  FIGURE
%%%%
\begin{figure}[ht] 
\vbox{
\hbox{\hspace{1.5cm}
\includegraphics[width=.85\textwidth]{./Pics1/mr1_fixed/mr1_fixed_middle_1.pdf} 
}
\vspace{0.0cm}
\hbox{\hspace{4.0cm} (a) MR1 at t = 3000 (end)   
}
\vspace{0.25cm}
\hbox{\hspace{1.5cm}
\includegraphics[width=.85\textwidth]{./Pics1/mr10_fixed/mr10_fixed_middle_1.pdf}
}
\vspace{0.0cm}
\hbox{\hspace{4.0cm} (b) MR10 at t = 3000 (end)  
}
}     
\caption{Comparing the the MR1 and MR10 cases using fixed mesh in the end of the simulation.}
\label{fig:6c}
\end{figure}
\clearpage
\end{comment}

%%%%
%%%%  FIGURE
%%%%
\begin{landscape}
\begin{figure}[ht] 
\vbox{\vspace{-1cm}
\hbox{\includegraphics[width=.7\textwidth]{./Pics1/Saffman_homogeneous_MR3/saffman_homo_fixed_2.pdf}
      \includegraphics[width=.37\textwidth]{./Pics1/Saffman_homogeneous_MR3/saffman_homo_fixed_250.pdf}
      \includegraphics[width=.37\textwidth]{./Pics1/Saffman_homogeneous_MR3/saffman_homo_fixed_1000.pdf}}
\vspace{0.cm}
\hbox{\hspace{2.0cm} (a) pressure at t=0 \hspace{5.cm} (b) t=250\red{(???)} \hspace{2.75cm} (c) t=1000\red{(???)}}
\vspace{0.5cm}
\hbox{
      \includegraphics[width=.375\textwidth]{./Pics1/Saffman_homogeneous_MR3/saffman_homo_fixed_2500.pdf}
      \includegraphics[width=.375\textwidth]{./Pics1/Saffman_homogeneous_MR3/saffman_homo_fixed_3500.pdf} 
      \includegraphics[width=.65\textwidth]{./Pics1/Saffman_homogeneous_MR3/saffman_homo_fixed_end.pdf}}
\vspace{0.cm}
\hbox{ \hspace{1.cm} (d) t=2500\red{(???)} \hspace{2.0cm} (e) t=1000\red{(???)}   \hspace{3.0cm} (f) t=XXX\red{(???)}}
\vspace{0.cm}
}   
\caption{Simulated flow in a Hele-Shaw cell ({\it VR}=3): (a) pressure profile $\left(\text{in g.cm}^{-1}\text{.s}^{-2}\right)$ with source and sink regions are explicitly shown along with dimensions (in cm); (b-f) snapshots of wetting phase saturation showing flow profile as the simulation evolves. The domain contains $47500$ \PN[1]{2} triangular elements.}
\label{fig:homoheleshaw_VN3}
\end{figure}
\end{landscape}
\clearpage

%%%%
%%%%  FIGURE
%%%%
\begin{landscape}
\begin{figure}[ht] 
\vbox{\vspace{-1cm}
\hbox{\includegraphics[width=.5\textwidth]{./Pics1/Saffman_homogeneous/saffman_homo_fixed_1.pdf}
      \includegraphics[width=.5\textwidth]{./Pics1/Saffman_homogeneous/saffman_homo_fixed_250_1.pdf}
      \includegraphics[width=.5\textwidth]{./Pics1/Saffman_homogeneous/saffman_homo_fixed_1000.pdf}}
\vspace{0.cm}
\hbox{\hspace{1.0cm} (a) pressure at t=0 \hspace{3.cm} (b) t=250\red{(???)} \hspace{3.0cm} (c) t=1000\red{(???)}}
\vspace{0.5cm}
\hbox{
      \includegraphics[width=.5\textwidth]{./Pics1/Saffman_homogeneous/saffman_homo_fixed_6000.pdf}
      \includegraphics[width=.5\textwidth]{./Pics1/Saffman_homogeneous/saffman_homo_fixed_end_1.pdf}}
\vspace{0.cm}
\hbox{ \hspace{2.cm} (d) t=6000\red{(???)} \hspace{3.cm} (e) t=XXX\red{(???)}}
\vspace{0.cm}
}   
\caption{Simulated flow in a Hele-Shaw cell ({\it VR}=10): (a) pressure profile $\left(\text{in g.cm}^{-1}\text{.s}^{-2}\right)$ with source and sink regions explicitly shown along with dimensions (in cm); (b-e) snapshots of wetting phase saturation showing flow profile as the simulation evolves. The domain contains $47000$ \PN[1]{2} triangular elements. The pressure and saturation range of values are the same like the  case in fig.\ref{fig:homoheleshaw_VN3}.}
\label{fig:homoheleshaw_VN10}
\end{figure}
\end{landscape}
\clearpage

\begin{comment}
%%%%
%%%%  FIGURE
%%%%
\begin{figure}[ht] 
\vbox{
\hbox{\hspace{2.5cm}
\includegraphics[width=.6\textwidth]{./Pics1/Saffman_homogeneous_MR3/saffman_homo_fixed_1.pdf} 
}
\vspace{0.0cm}
\hbox{\hspace{4.0cm} (a) Hell-Shaw cell domain   
}
\vspace{0.25cm}
\hbox{\hspace{2.5cm}
\includegraphics[width=.6\textwidth]{./Pics1/Saffman_homogeneous_MR3/saffman_homo_fixed_250.pdf}
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (b) flow at t=250  
}
}     
\caption{This is a description of a Hele-Shaw experimental domain, showing the source and sink term as this is implied in this test-case followed by a screenshot of the flow at time, t=250(b). More screenshot follow that describe the progression of the flow in figure \ref{fig:1b_homoheleshaw_3} and figure \ref{fig:1c_homoheleshaw_3}.}
\label{fig:1a_homoheleshaw_3}
\end{figure}
\clearpage

%%%%
%%%%  FIGURE
%%%%
\begin{figure}[ht] 
\vbox{
\hbox{\hspace{2.5cm}
\includegraphics[width=.6\textwidth]{./Pics1/Saffman_homogeneous_MR3/saffman_homo_fixed_1000.pdf} 
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (a) flow at t=1000   
}
\vspace{0.25cm}
\hbox{\hspace{2.5cm}
\includegraphics[width=.6\textwidth]{./Pics1/Saffman_homogeneous_MR3/saffman_homo_fixed_2500.pdf}
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (b) flow at t=2500  
}
}     
\caption{Following figure \ref{fig:1a_homoheleshaw_3} as the flow progress, t=1000(a), a tip start to appears, at t=2500(b).}
\label{fig:1b_homoheleshaw_3}
\end{figure}
\clearpage

%%%%
%%%%  FIGURE
%%%%
\begin{figure}[ht] 
\vbox{
\hbox{\hspace{2.5cm}
\includegraphics[width=.6\textwidth]{./Pics1/Saffman_homogeneous_MR3/saffman_homo_fixed_3500.pdf} 
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (a) flow at t=3500   
}
\vspace{0.25cm}
\hbox{\hspace{2.5cm}
\includegraphics[width=.6\textwidth]{./Pics1/Saffman_homogeneous_MR3/saffman_homo_fixed_end_1.pdf}
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (b) flow at t=end  
}
}     
\caption{This tip will become sharper at t=3500(a) as it approaches the area where sink term exist and finally at t=end(b) it will be absorbed.}
\label{fig:1c_homoheleshaw_3}
\end{figure}
\clearpage

%%%%
%%%%  FIGURE
%%%%
\begin{figure}[ht] 
\vbox{
\hbox{\hspace{2.5cm}
\includegraphics[width=.6\textwidth]{./Pics1/Saffman_homogeneous/saffman_homo_fixed_1.pdf} 
}
\vspace{0.0cm}
\hbox{\hspace{4.5cm} (a) Hell-Shaw cell domain   
}
\vspace{0.25cm}
\hbox{\hspace{2.5cm}
\includegraphics[width=.6\textwidth]{./Pics1/Saffman_homogeneous/saffman_homo_fixed_250_1.pdf}
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (b) flow at t=250  
}
}     
\caption{This is a description of a Hele-Shaw experimental domain, when MR=$10$ showing the source and sink term as this is implied in this test-case followed by a screenshot of the flow at time, t=250(b). Screenshot will follow that describe the progression of the flow in figure \ref{fig:2b_homoheleshaw_10} and figure \ref{fig:2c_homoheleshaw_10}.}
\label{fig:2a_homoheleshaw_10}
\end{figure}
\clearpage

%%%%
%%%%  FIGURE
%%%%
\begin{figure}[ht] 
\vbox{
\hbox{\hspace{2.5cm}
\includegraphics[width=.6\textwidth]{./Pics1/Saffman_homogeneous/saffman_homo_fixed_1000.pdf} 
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (a) flow at t=1000   
}
\vspace{0.25cm}
\hbox{\hspace{2.5cm}
\includegraphics[width=.6\textwidth]{./Pics1/Saffman_homogeneous/saffman_homo_fixed_4000.pdf}
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (b) flow at t=4000  
}
}     
\caption{As the flow progress at t=1000(a) the front still remains uniform. The first break down of the front is happening at t=4000(b) where $3$ tips start to come out of the main flow.}
\label{fig:2b_homoheleshaw_10}
\end{figure}
\clearpage
